\def\tenpg{1}
\def\twentyfive{0}
\def\thirty{0}
\if\tenpg1
\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\fi
\if\twentyfive1
\documentclass[12pt]{article}
\usepackage[margin=0.95in]{geometry}
\fi
\if\thirty1
\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\fi
\usepackage{bibentry}
\usepackage{bbm}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
 {hyperref}
\usepackage{verbatim}
\usepackage{appendix}
\usepackage{mathtools}
\usepackage{threeparttable}
\usepackage{url}
\usepackage[authoryear]{natbib}
\usepackage{tikz}
\usepackage{booktabs} %Package with \toprule, \midrule, \bottomrule
\usepackage{placeins} %Package with \FloatBarrier command
\usepackage{physics}
\usepackage[en-US]{datetime2}
\usepackage{setspace}
\newcommand{\sym}[1]{\rlap{#1}}

\hypersetup{
	pdftex,
    pdfauthor={Luke Motley},     % author
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=black,        % color of links to bibliography
    urlcolor=blue           % color of external links
}

% CUSTOM DEFINITIONS
\urldef{\dingelhomepage}\url{http://faculty.chicagobooth.edu/jonathan.dingel/}
\urldef{\dingelemail}\url{jdingel@chicagobooth.edu}
\newtheorem{proposition}{Proposition}

% IDENTIFYING INFORMATION
\title{Work from Home, School from Home: Teleworkability and COVID-induced Educational Inequalities}
\author{Luke Motley\thanks{Many thanks to Professor Andrew Garin for his willingness to supervise this project and his indispensable feedback along the way.} \\ University of Illinois at Urbana-Champaign}
\date{Completed in December 2020}


\begin{document}
\begin{titlepage}
\maketitle

\vspace{1.5cm}
{\Large
 Note: This submission is a sample of my undergraduate thesis, written in the Fall semester of 2020.
\\ \\
A full version of the paper and a replication package\footnote{The replication package uses \texttt{Makefiles} to reproduce every number, figure, and table in the paper from scratch, starting with the downloading of source datasets. It is executable with a single shell command, \texttt{make}. Though it is OS-independent, Stata is required. The linked GitHub page contains more detailed instructions and system requirements.} can be found at: \\
\href{https://github.com/ljmotley/FA20-Independent-Study}{https://github.com/ljmotley/FA20-Independent-Study}.
}

\end{titlepage}
\bibliographystyle{../bib/aeanobold-oxford}

% -----------------------------------------------
% 	ABSTRACT
% -----------------------------------------------

\begin{abstract}
\input{./sections/abstract.tex}
\end{abstract}
\vspace{1cm}
{\small
\noindent \textit{Keywords}:
Online learning,
Educational inequality,
COVID-19,
Google Trends,
Teleworkability
\\
\textit{JEL codes}:
I24,
I28,
J13,
J24
}
\thispagestyle{empty}
\newpage
\setcounter{page}{1}

% -----------------------------------------------
% 	BODY
% -----------------------------------------------

\if\tenpg0
\doublespacing
\fi
\input{./sections/intro.tex}
\input{./sections/background.tex}
\input{./sections/data.tex}
\input{./sections/methodology.tex}
\input{./sections/results.tex}
\input{./sections/discussion.tex}
\input{./sections/conclusion.tex}



% -----------------------------------------------
% 	REFERENCES
% -----------------------------------------------

\if\tenpg0
\clearpage
\bibliography{../bib/Paper.bib}{}
\fi
\if\tenpg1
{
\nobibliography{../bib/Paper.bib}{}
\vspace{0.5cm}
\Large \textbf{References, Additional Exhibits, and Appendix} \\
\large\textit{Omitted to meet the page requirements. Link to full paper on the first page.}
\fi


%\input{./sections/appendix_theory}
%\input{./sections/appendix_data.tex}
\if\tenpg0
\clearpage
\input{./sections/exhibits.tex}
\begin{center} \Large \textbf{Appendix -- For Online Publication} \end{center}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\input{./sections/appendix_exhibits.tex}
\else
\clearpage
\begin{center} \Large \textbf{Appendix -- For Online Publication} \end{center}
\input{./sections/exhibits.tex}
\input{./sections/appendix_exhibits.tex}

\textit{Note: Appendix omitted to meet the page requirements. Link to full paper on the first page.}
\fi

\end{document}
